---
title: "W_UP_01"
author: "Seth Guzman"
date: "fall 2020"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

The task of this statistical report is to find the average number of pushups preformed by skill and line players. The next part is to figure out if there is a difference in the average between both players


$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

The statistical analysis i will be using for this report is Num~Cat

pushups is classified as numerical 
player position is classified as categorical

The methods used to display the data will be a scatterplot, numerical summary and a t-test


# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
ggplot(data = mydata, aes(x = position, y = pushups)) +
  geom_point()
```


The scatter plots shows a difference in the average between skill players and line players
Skill players on average would perform 60 pushups while line players only performed 20>
Both players were given two minutes to complete the task of performing pushups


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```

This numerical table gives us a clearer look into the averages pulled from the data.
The mean of line players was 17 and for skill players it was 49 a significant difference.
We can infer that skill players outperform line players by 20 pushups


## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```

The P value equals 9.421e-06 meaning that its insignificant therefore disproving the null hypothesis $H_A$

The confidence interval confirms the previous inference of skill players outperforming the line players by 20-30 pushups


# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

By sorting through the data by using the methods listed in the introduction, ive found the mean of both players and have concluded there is in fact a difference between the two. The mean for line players was 17 and for skill players it was 47. Using the confidence interval we can see a difference of around 20-30 pushups being done on average.  